Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations

### 2019-09-14 notes/paper/paper.tex
added parameter talk

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ Fcross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

>>>>

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }
